Distance Sampling in \proglang{R}

### 2016-04-05 paper.Rmd
suppress nlme start message

```{r setup, include=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE)
```

@@

# generate some animals to sample
set.seed(15) # same results every time
library("mgcv", quietly=TRUE) # for inSide

>>>>

```{r setup, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(prompt = TRUE)
options(prompt = 'R> ')
```

@@

# generate some animals to sample
set.seed(15) # same results every time
suppressPackageStartupMessages(library("mgcv")) # for inSide
